```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(RSocrata)
library(ggplot2)
library(tidyverse)
```


```{r}
data =  read.socrata("https://data.cityofnewyork.us/Public-Safety/NYPD-Arrest-Data-Year-to-Date-/uip8-fykc")
```

First, we import the Year-to-Date, which is from January 1, 2022, to September 30, 2022, NYPD Arrest Data from NYC OpenData, where each row is an arrest effected in NYC by the NYPD with columns includeing information about the type of crime, the location and time of enforcement, and suspect demographics. Through the glimpse of the dataset, we found that this dataset is well-stored and well-structured.

```{r}
glimpse(data)
```

```{r}
head(data)
```

```{r}
data = data %>% select(-c(geocoded_column))
```

To transform the dataset into a tidy form for exploratory analysis, we drop the column called 'geocoded_column' since this column is a combination of the longitude coordinate as the x coordinate and the latitude coordinate as the y coordinate.

```{r}
table(data %>% select(c(age_group)))
```

In addition, we notice that the age groups are not classified evenly. Namely, the age groups are '<18', '18-24', '25-44', '45-64', and '65+', where the range of group '18-24' is only 6, while others' ranges are 19. However, the number of arrests in the age group of '18-24' is extremely large compared to other age groups. It is worth paying attention to and explicitly exploring that remarkable number in plots. Thus, we keep the categories of age unchanged. Therefore, our dataset is in a tidy form to do exploratory data analysis in R now.


