---
output:
  pdf_document: default
  html_document: default
---
# Data 

```{r setup, include=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


```{r}
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(forcats)
library(RSocrata)
library(redav)
library(UpSetR)
library(naniar)
```


## Sources
After deciding the topic of the project, all of our team members searched data together to find the most suitable one. We have found that, to identify the crime types, patterns and so on, we need to get some historical crime data. Also, the data released by government or other official department would be more reliable. Here we extract the arrest records data from New York OpenData (https://data.cityofnewyork.us/Public-Safety/NYPD-Arrest-Data-Year-to-Date-/uip8-fykc), which is a free public data source published by New York City agencies and other organizations. The data we will use is collected by the New York Police Department(NYPD), including information about the type of crime, the location, the demographics of perpetrators, and so on. The Office of Management Analysis and Planning extracts and reviews the data every quarter. The data is last updated on Oct 19, 2022. 

The dataset is categorized as public safety and contains 141,000 observations with 19 columns in a structured form. Each row represents an arrest effected in New York City by NYPD. The column shows the basic information about the arrest, including the time, location, and level of offense. At the same time, the dataset also contains descriptions of perpetrators, such as gender, age, race, etc. Based on these data, we can well accomplish our research goals.

To fully explored the arrest pattern, a single dataset is not reliable. Therefore, we collected historic data for arrests records from the same platform, New York OpenData,  (https://data.cityofnewyork.us/Public-Safety/NYPD-Arrests-Data-Historic-/8h9b-rp9u). This dataset has the same format as year-to-date data, making it easy to compare with each other. However, we found that this historic dataset was only updated on June 9, 2022 lastly, which has been covered by our primal dataset. Therefore, instead of using both datasets, we use only the primal one in our projects.

We can export the dataset in CSV format for offline use from New York OpenData. Then we can import and manipulate the CSV formatted data in R from the local path.

## Cleaning / transformation

```{r}
data =  read.socrata("https://data.cityofnewyork.us/Public-Safety/NYPD-Arrest-Data-Year-to-Date-/uip8-fykc")
```

```{r}
head(data)
```


## Missing value analysis

### Why analyse missing value?

In this section, we want to know the distribution of missing values in the original dataset. Through missing pattern analysis, we are able to get an overview of the missing logic and determine how to deal with these missing values. Whether to delete them directly or to approach them based on other non-missing values?

### Missing pattern

We start by analysis the missing pattern of the whole dataset.

```{r}
data["pd_desc"][data["pd_desc"] == "(null)"] <- NA
gg_miss_upset(data, nsets = 19)

```

The left-bottom bar chart shows the total number of missing values in each column. The right chart shows the intersection pattern of the missing value. From the chart above, we can find that among 19 column in original data set, only 3 columns (pd_cd, pd_desc, ky_cd) has missing value. 

    - pd_cd: Three digit arrest internal classification code.
    - pd_desc: The description of internal classification code
    - ky_cd: Three digit internal classification code (more general category than PD code)
    
Notice the relation among pd_cd, pd_desc and ky_cd, it is easy to understand the consistency of missing value. Since the Keycode is a more general category, if the Key code of an arrest event is unknown, the PD code also remains unknown. Similarly, if the PD code is unkown, we cannot describe it. 

### Missing borough analysis:


```{r}
missing_data <- data
missing_data["arrest_boro"][missing_data["arrest_boro"] == "Q"] <- "Queens"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "B"] <- "Bronx"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "S"] <- "Staten Island"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "K"] <- "Brooklyn"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "M"] <- "Manhattan"

gg_miss_var(missing_data,
            facet = arrest_boro
            ) +
  labs(x = "Column", title = "Missing values in different region")+
  theme_bw()

```

When faceted on borough, we were surprised to find that majority of missing values are derived from Queens.It is probably due to data filing errors in this region, or the peculiarities of some crimes. We wonder if these arrest belongs to same accident or have some relation.

```{r}
queens_data <- missing_data %>%
  filter(arrest_boro == "Queens") %>%
  filter(is.na(ky_cd))

ggplot(queens_data, aes(x=arrest_date)) +
  ggtitle("Missing value for Queens in 2022") +
  geom_histogram(color = "blue", fill = "lightBlue") +
  labs(x= "Month(2022)", y = "# missing value") +
  theme_bw()
```


We can propose a hypothesis from the charts above: Arrest data loss occurs throughout the year. There is no peak or obvious pattern, thus missing value is not due to specific incidents or periods, but it is highly likely because of the relatively poor system for arrest categorization in Queens.

### Way to deal with the missing value

```{r}
options(scipen = 9)
vis_miss(data,warn_large_data=FALSE)+
  labs(y = "rows",title = "Missing data overview")+
  theme(axis.text.x = element_text(angle=90))
  
```


Since we cannot induce the classification of the arrest from known data, and all missing data only account for a small part of the total data (0.27%), we decided to delete these data directly, which will not affect our follow-up data analysis.

