---
title: "result"
author: "JUNYUAN HUANG"
output:
  html_document:
    fig_width: 5
    fig_height: 3.5
  pdf_document: default
---

```{r setup, include=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


```{r}
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(forcats)
library(RSocrata)
library(redav)
library(UpSetR)
library(naniar)
library(ggmap)
```


```{r}
data =  read.socrata("https://data.cityofnewyork.us/Public-Safety/NYPD-Arrest-Data-Year-to-Date-/uip8-fykc")
```


```{r}
head(data)
```
### Arrest data look on map

In this section, we explore the arrest distribution look on map.

```{r}
missing_data <- data
missing_data["pd_desc"][missing_data["pd_desc"] == "(null)"] <- NA
missing_data["arrest_boro"][missing_data["arrest_boro"] == "Q"] <- "Queens"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "B"] <- "Bronx"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "S"] <- "Staten Island"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "K"] <- "Brooklyn"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "M"] <- "Manhattan"

map_data <- missing_data %>%
  filter(!is.na(ky_cd))

```


```{r}

map_queen <- map_data %>%
  filter(arrest_boro == "Queens")

map_bronx <- map_data %>%
  filter(arrest_boro == "Bronx")

map_si <- map_data %>%
  filter(arrest_boro == "Staten Island")

map_brooklyn <- map_data %>%
  filter(arrest_boro == "Brooklyn")

map_manhattan <- map_data %>%
  filter(arrest_boro == "Manhattan")

ny_map <- get_stamenmap(bbox = c(left = -74.2591, bottom = 40.4774, 
                                 right = -73.7002, top = 40.9162),
                        zoom = 10, maptype = "terrain",
                        color = c("color", "bw"))

map1 <- ggmap(ny_map) +
  geom_point(data = map_queen, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Queens") + 
  theme_bw()

map2 <- ggmap(ny_map) +
  geom_point(data = map_bronx, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Bronx") + 
  theme_bw()

map3 <- ggmap(ny_map) +
  geom_point(data = map_si, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Staten Island") + 
  theme_bw()

map4 <- ggmap(ny_map) +
  geom_point(data = map_brooklyn, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Brooklyn") + 
  theme_bw()

map5 <- ggmap(ny_map) +
  geom_point(data = map_manhattan, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Manhattan") + 
  theme_bw()

plot_grid(map1,map2,map3,map4,map5, labels = NULL, ncol = 3)

```

From the figure above, we can find that arrest happend in Manhattan, Bronx and Brooklyn is relatively concentrated. For Queens and Staten Island, there are places that never have an arrest during the whole year.

```{r}
map_data %>%
  mutate(Freq = 1) %>%
  group_by(arrest_boro) %>%
  summarise(freq = sum(Freq)) %>%
  ggplot(aes(x=fct_reorder(arrest_boro,freq,.desc = TRUE),y=freq)) +
  geom_bar(stat = "identity",fill = "#dea32c", color = "black", alpha = 0.8) +
  geom_text(aes(label=freq), size=3.5, vjust=1.6)+
  labs(title = "Borough-wise arrest in New York in 2022" , x="", y="Number of Arrest") +
  theme_bw()
```

It turns out that the number of arrests occurred in Staten Island is the least, which is about 1/3 of that in other borough.
