---
output:
  pdf_document: default
  html_document: default
---
# Results


```{r}
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(forcats)
library(RSocrata)
library(redav)
library(UpSetR)
library(naniar)
library(rvest)
library(ggpubr)
library(ggalluvial)
library(RColorBrewer)
library(choroplethr)
library(ggmap)
library(tmap)
library(scales)
library(cowplot)
library(ggmosaic)
library(lubridate)
```

## Criminals' portrait

We start to analyze the crime pattern with plotting the criminals' portrait.

With the arrest records, we plot the basic information namely age, gender and race for all perpetrators by histograms.

```{r}
data =  read.socrata("https://data.cityofnewyork.us/Public-Safety/NYPD-Arrest-Data-Year-to-Date-/uip8-fykc")
data <- data %>%
  drop_na(pd_desc, ky_cd, pd_cd)
```

```{r}
figure1 <- ggplot(data, aes(x=age_group))+ 
  geom_histogram(stat="count",position="identity", alpha=0.5, fill = "#dea32c")+
  coord_flip()+
  labs(caption="Figure.1 Age Distribution of the Criminals", 
       x="age", y="count")+ 
  theme(axis.text.y=element_text(size=8), axis.text.x=element_text(size=8))

figure2 <- ggplot(data, aes(x=perp_sex))+ 
  geom_histogram(stat="count",position="identity", alpha=0.5,fill = "#dea32c")+
  coord_flip()+
  labs(caption="Figure.2 Sex Distribution of the Criminals", 
       x="sex", y="count")+ 
  theme(axis.text.y=element_text(size=8), axis.text.x=element_text(size=8))

ggarrange(figure1, figure2, ncol = 2, nrow = 1)
```


```{r}
figure3 <- ggplot(data, aes(x=perp_race))+ 
  geom_histogram(stat="count",position="identity", alpha=0.5,fill = "#dea32c")+
  coord_flip()+
  labs(caption="Figure.3 Race Distribution of the Criminals", 
       x="race", y="count")+ 
  theme(axis.text.y=element_text(size=8), axis.text.x=element_text(size=8))

figure3
```

From the above three figures, we can observe the following characteristics of the captured criminals. First, the number of male perpetrators are highly greater than the number of female perpetrators. Even though the age group, as we mentioned in section 3.2 cleaning and transformation, is not evenly classified, the histogram of the distribution of age among perpetrators shows that the age of perpetrators is mainly concentrated in 25-44 years old. Beside, it is worth to notice that there are a remarkable amount of perpetrators only in their 18-24 years old. In addition, regarding the race distribution of perpetrators, the Black group and White Hispanic group are the two major group of perpetrators. These data and observations are useful to understand the demographics and biometrics of  perpetrators, and potentially helpful for NYPD and related researches on crimes in NYC.

### Relationship between sex, race and age

```{r}

race <- c("BLACK","BLACK HISPANIC", "ASIAN / PACIFIC ISLANDER","WHITE","WHITE HISPANIC","Others")

race_data <- data
race_data["perp_race"][race_data["perp_race"] == "AMERICAN INDIAN/ALASKAN NATIVE"] <- "Others"
race_data["perp_race"][race_data["perp_race"] == "UNKOWN"] <- "Others"
race_data$perp_race <- factor(data$perp_race, levels = race)
```

```{r}
ggplot(data = race_data) +
  geom_mosaic(aes(x = product(perp_race, age_group), fill = perp_sex),
              na.rm=TRUE,
              offset = 0.03)+
  labs(y="Race", x= "Age")+
  theme(axis.text.x= element_text(angle=-45),
        legend.title = element_blank())


```

From the mosaic plot above, we can see the age, gender, and race distribution of arrested people. Overall, males are the vast majority of all arrests. For age, the arrest rate of 25-44 is the highest among all age groups, followed by 18-24 and 45-60. With the weakening of activity, the arrest rate also decreases. For race, black and white Hispanics are the two main arrest groups, and the least arrested races are American Indian and Alaskan natives, which are categorized into "Others". Also, there is no strong pattern among age, race, and gender.


So there is another question: What is the connection between these criminals' figures and the specific types of crime correspondingly?

## Crime Types

First, we calculate the frequency of all crime types as shown in table below.

```{r}
cat_nyc <- select(data, ofns_desc)

crime_category_table <- table(cat_nyc$ofns_desc)
crime_category_table <- sort(crime_category_table, decreasing = TRUE)

crime_by_category <- as.data.frame(crime_category_table, stringsAsFactors = FALSE)
colnames(crime_by_category) <- c("Category", "Frequency")
crime_by_category$Percentage <- crime_by_category$Frequency / sum(crime_by_category$Frequency) * 100
crime_by_category 
```

We can see that there are 64 types of crimes in total. To have a clear and better understanding of the dataset, we select seven types of crimes which percentage is higher than 5% among the total observations for the further analysis. Then we can have a more explicit and concise plot to present the dataset. Otherwise, there would be a lot of chunks of data which is not very critical or meaningful on the plots.

They are [ASSAULT 3 & RELATED OFFENSES, PETIT LARCENY, FELONY ASSAULT, MISCELLANEOUS PENAL LAW, CRIMINAL MISCHIEF & RELATED OF, DANGEROUS DRUGS, ROBBERY].

```{r}
high_freq_crime_types <- data %>% filter((ofns_desc == "ASSAULT 3 & RELATED OFFENSES") | (ofns_desc == "PETIT LARCENY") | (ofns_desc == "FELONY ASSAULT") | (ofns_desc == "MISCELLANEOUS PENAL LAW") | (ofns_desc == "CRIMINAL MISCHIEF & RELATED OF") | (ofns_desc == "DANGEROUS DRUGS") | (ofns_desc == "ROBBERY") )

crime_by_category_plot <-ggplot(crime_by_category[1:7,], aes(x = Category, y = Frequency)) +     geom_histogram(stat="identity",alpha=0.5,fill = "#dea32c") + 
        labs(title = 'Crime by Category',
         x = 'Category',
         y = 'Frequency')+
    theme(axis.text.y=element_text(size=6), axis.text.x=element_text(size=4))
  
crime_by_category_plot
```


Here we made an mosaic diagram to show the relationship between the criminals and the crime types.

```{r}
library(ggmosaic)
library(vcd)
df_type <- select(high_freq_crime_types,c(age_group, perp_sex, ofns_desc))
color= brewer.pal(7,"Oranges")
vcd::mosaic(ofns_desc~age_group+perp_sex,df_type,direction=c('v','h','h'),highlighting_fill=color,alpha=0.5,fontsize=6, labeling = vcd::labeling_border(rot_labels = c(0, 0, 90, 0), abbreviate_labs = c(5, 1, 1)))+
      theme(axis.text.y=element_text(size=6), axis.text.x=element_text(size=4))
```

Here we can see that the distribution of different crime types is similar in different age groups and sex offenders. No pattern is observed from the mosaic graph. So there is no a strong assocation between the types of crime and the types of offenders.



Based on the analysis above, we can infer that there is a certain randomness between the crime rate and crime types. Therefore, the next question would be: are there any factors that are more strongly associated with crime rate in New York?

## Spacial Analysis

As we know, neighborhoods in New York are highly different among each other. Specifically, different regions in New York have highly various environments, house pricing, policing environments, different police forces, different people who live there. 

In this section, we look at the distribution of the number of arrests on map.

```{r}
missing_data <- data
missing_data["pd_desc"][missing_data["pd_desc"] == "(null)"] <- NA
missing_data["arrest_boro"][missing_data["arrest_boro"] == "Q"] <- "Queens"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "B"] <- "Bronx"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "S"] <- "Staten Island"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "K"] <- "Brooklyn"
missing_data["arrest_boro"][missing_data["arrest_boro"] == "M"] <- "Manhattan"

map_data <- missing_data %>%
  filter(!is.na(ky_cd))

```


```{r}

map_queen <- map_data %>%
  filter(arrest_boro == "Queens")

map_bronx <- map_data %>%
  filter(arrest_boro == "Bronx")

map_si <- map_data %>%
  filter(arrest_boro == "Staten Island")

map_brooklyn <- map_data %>%
  filter(arrest_boro == "Brooklyn")

map_manhattan <- map_data %>%
  filter(arrest_boro == "Manhattan")

ny_map <- get_stamenmap(bbox = c(left = -74.2591, bottom = 40.4774, 
                                 right = -73.7002, top = 40.9162),
                        zoom = 10, maptype = "terrain",
                        color = c("color", "bw"))

map1 <- ggmap(ny_map) +
  geom_point(data = map_queen, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Queens") + 
  theme_bw()

map2 <- ggmap(ny_map) +
  geom_point(data = map_bronx, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Bronx") + 
  theme_bw()

map3 <- ggmap(ny_map) +
  geom_point(data = map_si, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Staten Island") + 
  theme_bw()

map4 <- ggmap(ny_map) +
  geom_point(data = map_brooklyn, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Brooklyn") + 
  theme_bw()

map5 <- ggmap(ny_map) +
  geom_point(data = map_manhattan, aes(x=longitude, y = latitude),
             size=0.1,color='#b3424a', alpha = 0.1) +
  labs(x = "Longitude", y = "Latitude", title = "Manhattan") + 
  theme_bw()

plot_grid(map1,map2,map3,map4,map5, labels = NULL, ncol = 3)

```

From the figure above, we can observe that arrests which happened in Manhattan, Bronx and Brooklyn are relatively concentrated.In other words, in general, the crimes are possibly happened in any area in Manhattan, Bronx and Brooklyn. We could not say there is a certain region much safer than others in Manhattan, Bronx and Brooklyn. 
On Queens and Staten Island, the graphs indicate that there are some places that never have an arrest during the this current year.

```{r}
map_data %>%
  mutate(Freq = 1) %>%
  group_by(arrest_boro) %>%
  summarise(freq = sum(Freq)) %>%
  ggplot(aes(x=fct_reorder(arrest_boro,freq,.desc = TRUE),y=freq)) +
  geom_bar(stat = "identity",alpha=0.5,fill = "#dea32c", color = "black", alpha = 0.8) +
  geom_text(aes(label=freq), size=3.5, vjust=1.6)+
  labs(title = "Borough-wise arrest in New York in 2022" , x="", y="Number of Arrest") +
  theme()
```

By the bar plot of the number of arrests based on the borough of NYC, it turns out that the number of arrests occurred in Staten Island is the least consistent with the observation from the map graphs, which is about 1/3 of that in other borough.


```{r}
figure_boro <- ggplot(high_freq_crime_types, 
                  aes(x=arrest_boro,color=ofns_desc, 
                      fill=ofns_desc))+
  geom_histogram(stat="count",position="identity", bins = 100, alpha=0.5)+
  facet_grid(ofns_desc ~ .)+
  labs(caption="Figure.4 Types of Crimes by the Borough",
       x="Borough in NYC", y = "count")+
  theme_minimal()

figure_boro
```

This bar plot compares the number of various types of arrests based on the different boroughs of NYC. It is worth to notice that the number of Petit Larceny is relatively high in Manhattan compared to other types of crimes in NYC and the number of Petit Larceny in other boroughs. In general, there is no strong pattern between the types of crimes and the boroughs of the crimes, which are evenly distributed with proportions to their total number of crimes in boroughs.

## Temporal Analysis


We want to explore if there is any monthly or seasonal pattern over time by plotting the number of arrest over time. If crime is tied to activities, the period at which activities end may impact.

```{r}
df_arrest_daily <- data %>%
  mutate(Date = as.Date(arrest_date, "%Y/%m/%d")) %>%
  group_by(Date) %>%
  summarize(count = n()) %>%
  arrange(Date)
fig_daily_arrest <- ggplot(df_arrest_daily, aes(x = Date, y = count)) +
  geom_line(color = "#F2CA27", size = 0.5) +
  geom_smooth(color = "#1A1A1A") +
  # fte_theme() +
  scale_x_date(breaks = date_breaks("1 month"), labels = date_format("%h")) +
  labs(x = "Date of Arrest", y = "# of Arrests", title = "Daily Arrests from 01/01/2022 to 9/30/2022")
fig_daily_arrest
```

This figure shows the number of daily arrests from January 1 2022, to September 30 2022. We can see there is no strong pattern over time. Nevertheless, there is a small increasing during the beginning of 2022 and a slight decreasing around July and August. Paying attention to January 1, 2022, which is the New Year, we can't conclude that the number of arrests happened on January 1 is higher. The graph shows that the number of crimes is not strongly related to the activities and time.

Then we will try to examine if the number of arrests has association with the day of week. We first need to derive the day of week based on the date. Also with subgroups, we can verify if there is a latent factor.

```{r}
data$dayofweek <- wday(data$arrest_date, label=TRUE, abbr=FALSE)
df_weekday <- data %>%
  mutate(dayofweek=dayofweek, month=months(as.Date(data$arrest_date))) %>%
  group_by(dayofweek, month) %>%
  summarize(count = n()) %>%
  arrange(dayofweek)
df_weekday$month <- factor(df_weekday$month, levels = c('January', 'February', 'March', 'April', 'May', 'June', 'July', 'August', 'September'))
```


```{r}
plot <- ggplot(df_weekday, aes(x = month, y = dayofweek, fill = count)) +
  geom_tile() +
  scale_x_discrete(name = "Month" )+
  # fte_theme() +
  theme(legend.title = element_blank(), legend.position="top", legend.direction="horizontal", legend.key.width=unit(2, "cm"), legend.key.height=unit(0.25, "cm"), legend.margin=unit(-0.5,"cm"), panel.margin=element_blank()) +
  labs(x = "Month", y = "Day of Week of Arrest", title = "Number of Arrests in NYC in 2022, by Day of Week of Arrest") +
  scale_fill_gradient(low = "white", high = "#27AE60", labels = comma)
plot
```

By plotting the heatmap of the number of arrests in NYC over time categorized by the day of week, we can notice a pattern that there are more arrests during the weekday than during weekends, specifically on Tuesday, Wednesday and Thursday. Moreover, from the graph, we can see that in January and February, overall there are fewer arrests in NYC compared to other months.

We also want to examine if certain types of crime may be more time dependent. For example, more traffic violations when people leave work.


```{r}
data = data %>%
  mutate(month=months(as.Date(data$arrest_date)))
```

```{r}
df_top_crimes <- data %>%
  group_by(ofns_desc) %>% 
  summarize(count = n()) %>%
  arrange(desc(count))

df_crime <- data %>%
  filter(ofns_desc %in% df_top_crimes$ofns_desc[1:24]) %>%
  group_by(ofns_desc, dayofweek, month) %>% 
  summarize(count = n())

df_crime$month <- factor(df_crime$month, levels = c('January', 'February', 'March', 'April', 'May', 'June', 'July', 'August', 'September'))
```

```{r, fig.width = 10}
plot <- ggplot(df_crime , aes(x = month, y = dayofweek, fill = count)) +
  geom_tile() +
  scale_x_discrete(name = "Month" )+
  # fte_theme() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, size = 4))+
  labs(x = "Month", y = "Day of Week of Arrest", title = "Number of Arrests in NYC in 2022 by Category and Time of Arrest") +
  scale_fill_gradient(low = "white", high = "#2980B9") +
  facet_wrap(~ ofns_desc, nrow = 4)
plot
```


We can see there is no strong relation among the day of week and the type of crimes, which is consistent with the general pattern. That is there are more arrests during the weekdays in general. For the crime type with the highest frequency, assault and related offenses are not time dependent and there is no certain pattern.